paper2_resistance_mechanisms_mixtures

### 2016-06-30 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
tweak figs, move to end, add text

The changing frequency of insecticide resistance is a population genetic process that can be influenced by :

Parameter  | Description
------------------- | -------------------------------------------------------
1. Effectiveness | proportion of exposed insects with the susceptible allele that are killed by the insecticide
2. Exposure | proportion of the insect population that are exposed to the insecticide
3. Dominance | dominance of the resistance allele relative to the susceptible allele
4. Selection Coefficient  | selective advatange of resistance in the presence of the insecticide
5. Frequency  | frequency of resistance alleles within the population

@@

For single insecticide use, increasing the values of either effectiveness, exposure, dominance, or the selective advantage of RR, all lead to faster resistance (Figs a1-4). (In these four plots the value of the inputs not being varied are set at a constant 0.5).

```{r, eval=TRUE, echo=FALSE, fig.height=4}

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=phi.SS1_A0)) + 
         labs(colour = "effectiveness") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a1. Effectiveness effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

@@

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=exposure)) + 
         theme_bw() +
         labs(colour = "exposure") +
         coord_trans(y = "log10") +    
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a2. Exposure effect on single insecticide.")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}

  #this sets exposures according to whether insecticide1, 2 or mixture
  a <- setExposure(exposure=0.5, insecticideUsed='insecticide1')

@@

  #plotallele.freq.andy(listOut, locus="1", sex="mf_mean", add_legend=FALSE)

  # now doing a better way
  df_resist <- get_resistance(locus=1, listOut)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=h.RS1_A0)) + 
         theme_bw() +
         labs(colour = "dominance") +
         coord_trans(y = "log10") + 
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a3. Dominance effect on single insecticide.")

```{r, eval=TRUE, echo=FALSE, fig.height=4}

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=rr_restoration_ins1)) + 
         theme_bw() +
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

       ) # end print

  cat("Fig. a4. Selective advantage of RR effect on single insecticide.")

@@

When two insecticides are used the relative performance of a mixture strategy compared to sequential use is determined by the values of these four inputs.

With all control inputs set equal at 0.5 resistance arises slower for sequential than mixture (Fig. 1 A). Resistance to both insecticides in the mixture follow the same path and reach the threshold at the same time. When used in sequence the curve for each insecticide individually is steeper but, because they happen one after the other, it takes longer to reach the resistance threshold for both.

**Effectiveness of the insecticides**
A more effective insecticide prompts increased time-to-resistance when used in a mixture. This contrasts with the earlier result showing that when used in isolation a single insecticide prompts a shorter time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, B. Effectiveness of insecticide1 increased from 0.5 to 0.9"}
#fig.cap seems necessary to keep figs side by side

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab="", main='B.' )

@@

In a mixture the mechanism is that a more effective insecticide provides greater protection to the other. For example taking the previous scenario and increasing the effectiveness of one insecticide from 0.5 to 0.9 increases the time-to-resistance for the 2nd insecticide from around 45 to 75 generations (Fig. 1 B). In the plot you can see that resistance to insecticide1 (with the increased effectiveness) rises at a similar speed to Fig. 1A. In contrast resistance to insecticide2 increases more slowly initially. Once insecticide1 reaches it's resistance threshold (around 40 generations), the curve for insecticide2 becomes steeper. This can be explained by the mechanism that once insecticide1 has become ineffective due to resistance it stops killing indivduals that are resistant to insecticide2 and thus stops 'protecting' it from it's own rise in resistance.

When the effectiveness of both insecticides are increased to 0.9 the time-to-resistance is increased still further to around 125 generations (Fig. 2). In this case the curves for the rise in resistance to each insecticide are identical. The curves are shallower than previous plots because individuals that are resistant to each insecticide are being killed by the other thus reducing the increase in resistance alleles. As the resistance frequencies go above 10% around generation 100 both insecticides provide less protection to the other and the slope of the resistance curve increases.

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="Effectiveness of both insecticides 0.9"}

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )

@@

**Dominance of resistance alleles**
Increasing the dominance of the alleles within a mixture has the same direction of effect as it does for sole use. Increasing the dominance of the allele corresponding to insecticide1 from 0.5 to 0.9 decreases the time-to-resistance to insecticide1 from 40 to 30 generations but leaves the time-to-resistance for the mixture the same (Fig. 3A). Setting the dominance for both alleles to 0.9 reduces the time-to-resistance for the mixture to 30 generations (Fig. 3B). In both of these cases sequential use continues to have a longer time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Dominance of insecticide1 0.9, B. Dominance of both insecticides 0.9"}

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )
#cat("Dominance of insecticide1 0.9")

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', main='B.' )
#cat("Dominance of both insecticides 0.9")

@@

**Selective advantage of resistance**
#TODO replace Figs 6,7,8 with AA,BB,CC below and modify this text
Decreasing the selective advantage of resistance to insecticide1 from 0.5 to 0.1 increases it's time-to-resistance in the mixture from 40 generations to 150, and has a similar effect on it's use in isolation (Fig. 6). However, it has little effect on resistance to insecticide2. Because of this sequential use continues to generate a longer time-to-resistance than the mixture. Decreasing the selective advantage of both alleles to 0.1 results in a longer time-to-resistance of 200 generations for the mixture (Fig. 7), however the relative shape of the resistance curves remains the same as in Fig. 1, with sequential use continuing to generate longer time-to-resistance.

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

Taking this scenario of lower selective advantage and increasing the effectiveness of both insectides from 0.5 to 0.7 shows again how the change in effectiveness has a greater effect on the mixture than sequential making the mixture preferable (compare Fig. 8 to Fig. 7).

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

#cool contrast between these scenarios modifying effectiveness and rr_restoration in which all defaults set to 0.5 except
TODO incorporate this into text above

#AA effectiveness I1 to 0.8 causes mixture to be slower, although I1 is faster it protects I2 in mixture, making mixture slower
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. AA. effectiveness to 0.8")
```

#BB rr advantage I1 to 0.8 sequential remains slower, although I1 is faster as in previous it provides less protection to I2 in the mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. BB rr_restoration I1 0.8")
```

#CC rr advantage I2 to 0.2 sequential remains slower (just), I2 slower than I1 in mixture similar to AA but receives less protection in mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.2 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. CC. rr_restoration I2 0.2")
```

**Exposure**
Increasing exposure to 0.9 reduces time-to-resistance for both mixture and sequential scenarios (Fig. 9). The change in exposure has a greater effect on the mixture relative to the sequential strategy and this results in a greater relative benefit for sequence versus mixture. Setting the effectiveness of both insecicides to 0.7 (while keeping all other inputs at 0.5) results in mixture being slightly favoured (Fig. 10), then making the increase in exposure from 0.5 to 0.9 results in a switch to sequential being the favoured strategy (Fig. 11). This demonstrates how higher exposures can favour sequential use.

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```

**single insecticide**

Parameter to increase  | effect on resistance | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | faster | increased deaths of susceptibles
2. Exposure | faster | increased deaths of susceptibles
3. Dominance | faster | increased survival of heterozygotes
4. Selective advantage | faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**mixture**

Parameter to increase  | effect on resistance | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | **slower** | increased deaths of individuals resistant to the other insecticide
2. Exposure | faster (but not as fast as for single) | increased deaths of individuals resistant to the other insecticide
3. Dominance | faster | increased survival of resistants
4. Selective advantage | ?faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**difference between mixture and sequential use**

Parameter to increase  | relative performance mix versus seq | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | mixture | faster resistance for single use and slower resistance in mixture
2. Exposure | sequence | faster resistance for mixture and sequence but has a greater effect on mixture
3. Dominance | ? | ?
4. Selective advantage | ? | ?
5. Frequency  | ? | ?

1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? Is it because the exposure to one insecticide also effects the development of resistance in the other ?
1. create some code to enable plotting 2 scenarios side-by-side
1. re-read GPIRM
1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. look at effect of sex linkage

>>>>

The changing frequency of insecticide resistance is a population genetic process that can be influenced by the parameters outlined in Table 1.

**Table 1. Parameters inflencing the development of insecticide resistance**

Parameter  | Description
------------------- | -------------------------------------------------------
1. Effectiveness | proportion of exposed insects with the susceptible allele that are killed by the insecticide
2. Exposure | proportion of the insect population that are exposed to the insecticide
3. Dominance | dominance of the resistance allele relative to the susceptible allele
4. Resistance restoration  | ability of resistance to restore fitness in the presence of the insecticide
5. Frequency  | frequency of resistance alleles within the population

@@

For single insecticide use, faster resistance resulted from higher values of any of the inputs outlined in Table 1, namely effectiveness, exposure, dominance, the resistance restoration coefficient, and starting frequencies of resistance (Figs 1-3). In these plots each input was varied in isolation with the others set at a constant 0.5, or 0.01 for starting frequency of resistance.

When two insecticides are used the relative performance of a mixture strategy compared to sequential use is determined by the values of these inputs. To help us understand the mechanisms influencing this relative performance we started with a single base scenario and investigated changing inputs indivividually. For our base scenario we set the values for the first four inputs in Table 1 to 0.5 and the starting frequencies of resistance to 0.1. For this base scenario resistance arises slower for sequential than mixture (Fig 4A). This plot, and those that follow, compares mixture and sequence for a single input scenario (where the previous plots showed 3 input scenarios). Resistance to both insecticides in the mixture follow the same path and reach the threshold at the same time. When used in sequence the curve (dashed) for each insecticide individually is steeper but, because they happen one after the other, it takes longer to reach the resistance threshold for both.

### Insecticide effectiveness
A more effective insecticide prompts increased time-to-resistance when used in a mixture. This contrasts with the earlier result showing that when used in isolation a single insecticide prompts a shorter time-to-resistance.

For example taking the base scenario and increasing the effectiveness of one insecticide from 0.5 to 0.8 increases the time-to-resistance for the mixture and decreases that for the sequence (Fig 4B). In the mixture resistance to insecticide1 (with the increased effectiveness) rises at a similar speed to the base scenario (Fig 4A).

When the effectiveness of both insecticides are increased to 0.8 the time-to-resistance is increased still further to around 125 generations (Fig 5). In this case the curves for the rise in resistance to each insecticide are identical. The curves are shallower than previous plots because individuals that are resistant to each insecticide are being killed by the other thus reducing the increase in resistance alleles. As the resistance frequencies go above 10% around generation 100 both insecticides provide less protection to the other and the slope of the resistance curve increases.

### Exposure
Increasing exposure to 0.8 reduces time-to-resistance for both mixture and sequential scenarios (Fig 6A relative to 4A). The change in exposure has a greater effect on the mixture relative to the sequential strategy and this results in a greater relative benefit for sequence versus mixture. Remembering that earlier increasing one effectiveness to 0.8 resulted in mixtures being favoured over sequence (Fig 4B). Increasing exposure from 0.5 to 0.8 switches back to sequential being the favoured strategy (Fig 6B). This demonstrates how higher exposures can favour sequential use.

### Dominance of resistance alleles
Increasing the dominance of the alleles within a mixture has the same direction of effect as it does for sole use. Increasing the dominance of the allele corresponding to insecticide1 from 0.5 to 0.8 decreases the time-to-resistance to insecticide1 within the mixture but leaves the time-to-resistance for the second insecticide in the mixture the same (Fig 7A). Setting the dominance for both alleles to 0.8 reduces the time-to-resistance for both the mixture and the sequence by 20 generations from the base scenario (compare Fig 7B to 4A). In both of these cases sequential use continues to have a longer time-to-resistance under the higher dominance.

### Resistance restoration coefficient
Increasing the resistance restoration coefficient to insecticide1 from 0.5 to 0.8 decreases the time-to-resistance for insecticide1 in the mixture, and has a similar effect on it's use in the sequence (Fig 8A). However, it has little effect on resistance to insecticide2. Because of this sequential use continues to generate a longer time-to-resistance than the mixture. Increasing the resistance restoration coefficient of both alleles to 0.8 results in a shorter time-to-resistance  for the mixture (Fig 8B), however the relative shape of the resistance curves remains similar to the base scenario  (Fig 4A), with sequential use continuing to generate longer time-to-resistance.

### Starting frequencies of resistance
Changing the starting frequency of resistance had a similar effect on time to resistance for both sequences and mixtures and thus had little effect on their relative performance. For example taking the base scenario and reducing the starting frequency of one resistance allele did not change from sequence being favoured (compare Fig 9A to Fig 4A). Similarly taking the base scenario with effectiveness of the first insecticide increased to 0.8 (Fig 4B) and decreasing starting frequency of that resistance allele did not result in the mixture being favoured (Fig 9B).

Higher values of all of the inputs lead to faster resistance when the insecticide was used singly. This can be explained by different mechanisms (see Table 2 for summary). [write more about this here]

[explain the effectivenes result, referring to Fig 4B versus 4A]
In contrast, resistance to insecticide2 increases more slowly initially. Once insecticide1 reaches it's resistance threshold, the curve for insecticide2 becomes steeper. This can be explained by the mechanism that once insecticide1 has become ineffective due to resistance it stops killing indivduals that are resistant to insecticide2 and thus stops 'protecting' it from it's own rise in resistance.

[Summary tables to refer to from discussion.]

**Table 2. Effect of inputs on resistance when insecticides used singly or in sequence**

Parameter to increase  | effect on resistance | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | faster | increased deaths of susceptibles
2. Exposure | faster | increased deaths of susceptibles
3. Dominance | faster | increased survival of heterozygotes
4. Resistance restoration | faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**Table 3. Effect of inputs on resistance when insecticides used in a mixture**

Parameter to increase  | effect on resistance | Mechanism
------------------ | --------- | ---------------------------------------------------
1. Effectiveness | **slower** | increased deaths of individuals resistant to the other insecticide
2. Exposure | faster (but less than for single) | increased deaths of individuals susceptible to one insecticide increases selection pressure for that resistance. However at the same time selection pressure is reduced by higher deaths of resistant individuals caused by the other insecticide.
3. Dominance | faster | increased survival of resistants
4. Resistance restoration | faster | increased survival of resistants
5. Frequency  | faster | less change needed to reach resistance threshold

**Table 4. Effect of inputs on the difference between mixture and sequential use**

Parameter to increase  | increase favours mix or sequence | Mechanism
------------------ | ------- | ---------------------------------------------------
1. Effectiveness | mixture | Higher effectiveness gives faster resistance for sequence and slower resistance in mixture
2. Exposure | sequence | Higher exposure gives faster resistance for sequence and mixture but the greater effect on mixture favours sequence.
3. Dominance | neither | Higher dominance gives faster resistance in both sequences and mixtures such that the difference between them is not changed. 
4. Resistance restoration | neither | As for dominance. Higher resistance restoration gives faster resistance in both sequences and mixtures such that the difference between them is not changed.
5. Frequency  | neither | As for dominance and resistance restoration. Higher starting frequencies give faster resistance in both sequences and mixtures such that the difference between them is not changed.

1. what plots might I want to show for starting frequency ?
1. work out what's going on with exposure ... why does increasing exposure have a greater effect on mixture than sequential ? Is it because the exposure to one insecticide also effects the development of resistance in the other ?
1. In discussion and maybe elewhere address potential concern that the relationships shown here may not hold for all of paramter space.
1. re-read GPIRM
1. can I develop explanatory diagrams to describe the input parameters ?
1. mention generation time of 1 month
1. mention other potential effects e.g. differential exposure of M&F, sex linkage, ...

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3, fig.show='hold', fig.align='left', fig.cap="Effect of inputs on single insecticide use. A. Effectiveness, B. Exposure"}

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=factor(phi.SS1_A0))) + 
         theme_bw() +  
         theme(legend.position = "bottom", legend.key = element_blank()) + 
         guides(colour = guide_legend(reverse=TRUE)) +  
         labs(colour = "effectiveness") +
         coord_trans(y = "log10") +    
         geom_line()

       )

@@

  input <- cbind(i1,i2,i3)

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=factor(exposure))) + 
         theme_bw() +
         theme(legend.position = "bottom", legend.key = element_blank()) + 
         guides(colour = guide_legend(reverse=TRUE)) +
         labs(colour = "exposure", y=NULL) +
         coord_trans(y = "log10") +   
         geom_line()

       )

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3, fig.show='hold', fig.align='left', fig.cap="Effect of inputs on single insecticide use. A. Dominance, B. Resistance restoration"}

  #single insecticide dominance fig

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=factor(h.RS1_A0))) + 
         theme_bw() +
         theme(legend.position = "bottom", legend.key = element_blank()) + 
         guides(colour = guide_legend(reverse=TRUE)) + 
         labs(colour = "dominance") +
         coord_trans(y = "log10") + 
         geom_line()

       )

  # single insecticide resistance restoration fig.

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=factor(rr_restoration_ins1))) + 
         theme_bw() +
         theme(legend.position = "bottom", legend.key = element_blank()) + 
         guides(colour = guide_legend(reverse=TRUE)) +
         labs(colour = "rr restoration", y=NULL) +
         coord_trans(y = "log10") +   
         geom_line()   
       )

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3, fig.show='hold', fig.align='left', fig.cap="Effect of resistance starting frequency on single insecticide use."}

  #single insecticide frequency fig

  i1 <- setInputOneScenario( max_gen = 500,
                      P_1 = 0.001,       
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      P_1 = 0.01,       
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      P_1 = 0.1,       
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  input <- cbind(i1,i2,i3)

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=factor(P_1))) + 
         theme_bw() +
         theme(legend.position = "bottom", legend.key = element_blank()) + 
         guides(colour = guide_legend(reverse=TRUE)) + 
         labs(colour = "start\nfrequency") +
         coord_trans(y = "log10") + 
         geom_line()

       )
```

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. All control inputs equal at 0.5, B. Effectiveness of insecticide1 increased from 0.5 to 0.8"}
#effectiveness on mixture

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab="", main='B.' )

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="Effectiveness of both insecticides 0.8"}

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Exposure increased to 0.8, B. Exposure and Effectiveness of insecticide1 increased from 0.5 to 0.8"}
#fig.cap seems necessary to keep figs side by side

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )
#cat("Fig. Exposure 0.8 benefit of sequence over mixture increases")

@@

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), main='B.' )
#cat("Fig. Effectiveness 0.8, Exposure 0.8, increased exposure nullifies the effect of increased effectiveness, sequence remains better")
```

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Dominance of insecticide1 0.8, B. Dominance of both insecticides 0.8"}

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )
#cat("Dominance of insecticide1 0.8")

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.8 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', main='B.' )
#cat("Dominance of both insecticides 0.8")

@@

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Resistance restoration coefficient allele1 0.8, B. Resistance restoration coefficient both alleles 0.8"}

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )
#cat("Fig. rr_restoration I1 0.8")

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.8 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', main='B.' )
#cat("Fig. CC. rr_restoration I2 0.2")

```{r, eval=TRUE, echo=FALSE, fig.height=3.7, fig.width=3.7, fig.show='hold', fig.align='left', fig.cap="A. Start frequency allele1 reduced from 0.001, B. as A plus effectiveness insecticide1 increased to 0.8"}

#P_1 to 0.001 seq remains better
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), addLegend=FALSE, main='A.' )

#P_1 to 0.001 & effect1 to 0.8 mix remains better
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2'), ylab='', main='B.' )
